The Post-2007 Declining U.S. Birth Rates imply Significant Societal Shifts in the U.S.

### 2023-02-21 outputs/paper/paper.qmd
Update paper to include some analysis, and references to fix minor errors

```{r}
#| label: fig-1
#| fig-cap: Trends in U.S. Birth rates of 1000 women between age 14 to 44 from 1980 to 2020
#| echo: false
fig1_data <- read.csv(here::here("inputs/data/fig_1.csv"))
fig1_data %>%
  ggplot(aes(x = year,
             y = brate_all)) +
  geom_line() +
  scale_y_continuous(limits = c(50, 80), breaks = seq(50, 80, by = 5)) +
  labs(
    title = "Trend in US Birth Rates",
    x = "Years",
    y = "Births per 1,000 women age 15-44",
    caption = "Source: Birth Rates collected from CDC Vital Statistics Births Reports for 2015, 2019 and 2020."
  )  +
  theme_light()
```

@@

```{r}

```
Figure 4. place it here with Figure 7
```{r}

@@

```{r}
#| label: fig-billss
#| fig-cap: Relationship between Changes in Birth Rates 2004-2008 to 2014-2019
#| echo: false
#| fig-width: 8
#| fig-height: 4

@@

```{r}
#| label: fig-billsss
#| fig-cap: Trends in Birth Rates by Population subgroup Five-year age group
#| echo: false
#| fig-width: 8
#| fig-height: 4

@@

```{r}
#| label: fig-4
#| fig-cap: cohorts
#| echo: false
nch_cohot_data <- read_dta(here::here("inputs/data/nchs/nchs_cohort_analysis.dta"))
agecomp_data <- read_dta(here::here("inputs/data/pop/agecomp-seer.dta"))

>>>>

```{r}
#| label: fig-1
#| fig-cap: Trends in U.S. Birth rates of 1000 women between age 15 to 44 from 1980 to 2020
#| messages: false
#| echo: false
#| warning: false
#| 
fig1_data <- read.csv(here::here("inputs/data/fig_1.csv"))
fig1_data %>%
  ggplot(aes(x = year,
             y = brate_all)) +
  geom_line() +
  scale_y_continuous(limits = c(50, 80), breaks = seq(50, 80, by = 5)) +
  labs(
    title = "Trend in US Birth Rates",
    x = "Years",
    y = "Births per 1,000 women age 15-44",
    caption = "Source: Birth Rates collected from CDC Vital Statistics Births Reports for 2015, 2019 and 2020."
  )  +
  theme_light()
```
@fig-1 shows that overtime, the number of births in the United States is dropping steadily, while it slightly went up on peak around 1990, 2001, and 2007. Most likely the hikes of going up during these years might have been into other factors that made more people among the selected population to have kids. After 2007, the number of births drastically dropped a lot. Nowadays, among 1,000 women from age 15 to 44, only about 56 births will occur. While, in the past around the 1980s, and 1990s, the number of births was around 65 to 70 range. The line in the graph shows that in the near future much lower amount of people will have kids, and this can be due to other factors from their lifestyle which is making them to decide to not have more kids.

@@

```{r}
#| messages: false
#| echo: false
#| warning: false

```
Figure 4. place it here with Figure 7
```{r}
#| messages: false
#| echo: false
#| warning: false

@@

```{r}
#| label: fig-billss
#| fig-cap: Relationship between Changes in Birth Rates 2004-2008 to 2014-2019
#| messages: false
#| echo: false
#| warning: false
#| fig-width: 8
#| fig-height: 4

@@

```{r}
#| label: fig-billsss
#| fig-cap: Trends in Birth Rates by Population subgroup Five-year age group
#| messages: false
#| echo: false
#| warning: false
#| fig-width: 8
#| fig-height: 4

@@

```{r}
#| label: fig-4
#| fig-cap: cohorts
#| messages: false
#| echo: false
#| warning: false
nch_cohot_data <- read_dta(here::here("inputs/data/nchs/nchs_cohort_analysis.dta"))
agecomp_data <- read_dta(here::here("inputs/data/pop/agecomp-seer.dta"))
